---
title: "Predict Customer Churn with Artificial Neural Network Algorithm"
output: github_document
---



We will use ANN algorithm to predict if the bank customer will stay at the bank or churn out.
The dependent variable Exited has two values. 1 means exited, 0 means stays at the bank.


```{r}
# Importing the dataset
dataset = read.csv('Churn_Modelling.csv')
head(dataset)
```

We will choose the variables which can has an impact on dependent variable.
```{r}
dataset = dataset[4:14]
head(dataset)
```


```{r}
# Encoding the categorical variables as factors
dataset$Geography = as.numeric(factor(dataset$Geography,
                                      levels = c('France', 'Spain', 'Germany'),
                                      labels = c(1, 2, 3)))
dataset$Gender = as.numeric(factor(dataset$Gender,
                                   levels = c('Female', 'Male'),
                                   labels = c(1, 2)))
str(dataset)
```


```{r}
# Splitting the dataset into the Training set and Test set
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(dataset$Exited, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```


```{r}
# Feature Scaling
training_set[-11] = scale(training_set[-11]) # scale all variables except dependent variable
test_set[-11] = scale(test_set[-11])
```

Fitting ANN to the Training set
```{r}
# install.packages('h2o')
library(h2o)
h2o.init(nthreads = -1) # allows you to connect specific server you need for ANN model
model = h2o.deeplearning(y = 'Exited', # dependent variable
                         training_frame = as.h2o(training_set), # convert training set to a H2O frame
                         activation = 'Rectifier',
                         hidden = c(5,5), # I choose 5 neural networks. Practically choose the half number of independent variables. We have 10 independent variables. So I choose 5 for it.
                         epochs = 100,
                         train_samples_per_iteration = -2) # -2 autotunes the model
```
## Note: Since we are connected to a server, building of this model will take shorter time than it takes in python. This is the advantage of H2O package.


```{r}
# Predicting the Test set results
y_pred = h2o.predict(model, newdata = as.h2o(test_set[-11])) # predicts the probability of customer exited.
y_pred = (y_pred > 0.5)  # if probability greater than 0.5 then customer exits. Otherwise stays at the bank.
```
## Note: If you predict a sensitive information like if the tumour is benign or malignent, you can take higher threshold value a higher number like  0.8 


```{r}
y_pred = as.vector(y_pred) # We convert daataset to vector as we need vector for implementing confusion matrix

# Making the Confusion Matrix
cm = table(test_set[, 11], y_pred)
cm
```


```{r}
Accuracy = (1535+203) / 2000
# Note: We got an accuracy of 0.869 which is wonderfull. If we do k fold cross validation we can get better accuracy.
```


```{r}
h2o.shutdown() # disconnects from server
```

